Texture Mapping 3D Models of Indoor Environments with Noisy Camera Poses

### 2012-06-29 3dimpvt/_region_.tex
references in, too long

\message{ !name(paper.tex) !offset(509) }
\begin{figure}
  \centering
  \subfloat[][]{\includegraphics[width=1in]{projectionWall.pdf}}
  \centering
  \subfloat[][]{\includegraphics[width=1.1in]{projectionCeiling.pdf}}
  \centering
  \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
  \caption{(a): Undistorted fisheye images for vertical planes are
    tilted, but their effective camera axis is more or less normal to
    the plane. (b): The effective camera axis for ceilings is at an
    angle with respect to the plane normal. (c): Wall images are
    cropped to be rectangular.}
  \label{fig:projectionAngles}
\end{figure}
\message{ !name(paper.tex) !offset(734) }

>>>>

\message{ !name(paper.tex) !offset(200) }
\begin{figure}
  \centering
  \subfloat[][]{\includegraphics[width=3in, clip=true]{wall1_naive.jpg}}

  \centering
  \subfloat[][]{\includegraphics[width=3in, clip=true]{wall1_cache.jpg}}

  \centering
  \subfloat[][]{\includegraphics[width=3in, clip=true]{wall1_cache_shift.jpg}}

  \centering
  \subfloat[][]{\includegraphics[width=3in, clip=true]{wall1_dynprog_noblend.jpg}}

  \centering
  \subfloat[][]{\includegraphics[width=3in, clip=true]{wall1_cache_shift_blend.jpg}}

  \centering
  \subfloat[][]{\includegraphics[width=3in, clip=true]{wall1_dynprog.jpg}}
  \caption{(a) Direct mapping. (b) Mapping with caching. (c) Mapping
    with caching after image alignment. (d) Seam minimization after
    image alignment). (e) same as (c) with blending. (f) same as (d)
    with blending.}
  \label{fig:compareAll}
\end{figure}
\message{ !name(paper.tex) !offset(715) }
